---
title: "title"
description: |
  If you clicked on this link, guess my project was a success
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(tidyr)
library(dplyr)
library(rmarkdown)
```

## Breaking down the Data
# Investigation 1 - The Almighty Words of Fake News Headlines

### [Data](https://github.com/BuzzFeedNews/2018-12-fake-news-top-50)
Here is a short sample of data if you want to scroll through, sorted by the amount of Facebook likes they garnered. 


```{r, table}
titledata <- read.csv("newstitle1.csv")
paged_table(titledata)
```

### First Investigation: Most popular words
 
<div>
After going through ~7900 headlines, these are the most popular words! It's extremely fascinating, I know. 
</div>


```{r, first graph}
titledata %>%
  select(title, category) %>%
  slice(1:7900) %>% 
  mutate(title = strsplit(as.character(title), " ")) %>% 
  unnest(title) %>% 
  group_by(title) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  slice(1:10) %>% 

ggplot(mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines", 
     subtitle = "Wow! What a diverse range of words, could totally make a headline out of it!", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```
<div>
Hmm... Something about this graph doesn't seem right. Let's clean this data up by removing duplicates, punctuation, and prepositions! That'd give us a better idea of what people enjoy to read about, and allow us to find the best subject to center our article around!
</div>

```{r}
titledata <- read.csv("newstitle1.csv")
removedata <- titledata %>%
  select(title, category) %>%
  slice(1:7900) %>%
  mutate(title = strsplit(as.character(title), " ")) %>%
  unnest(title) %>%
  group_by(title) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>%
  slice(1:50)

newdata <- removedata[c(4, 15, 16, 17, 21, 25, 28, 29, 30, 37),]
ggplot(newdata, mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines (Edited)",
     subtitle = "Painfully obvious what year this is from", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```
<div>
Now, this just SCREAMS 2018. Let's get away from all the specific events that happened this year (mainly just the election) and see what other interesting stuff we can find, so that it's belivable any time of the year
</div> 

  