---
title: "Analyzing Fake News"
description: |
  If you clicked on this link, guess my project was a success
site: distill::distill_website
---
## Introduction
Alas, what have you stumbled into? 

# Goals 
Discover how to make the optimal fake news title, or basically, what makes a fake news article good?

Checklist:
1. What words do they use? What topics do they talk about? 
2. What about the length of the sentence? 

### Details 
How can I analyze fake news titles? 
Just because I think that the wording of a headline is crucial, is that actually true? 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(tidyr)
library(dplyr)
library(rmarkdown)
library(knitr)
library(plotly)
```

## Breaking down the Data
# Investigation 1 - The Almighty Words of Fake News Headlines

### [Data](https://github.com/BuzzFeedNews/2018-12-fake-news-top-50)
Here is a short sample of data if you want to scroll through, sorted by the amount of Facebook likes they garnered. 


```{r, table}
titledata <- read.csv("newstitleint.csv")
paged_table(titledata) %>% 
 mutate_at(vars(fb_engagement),
            as.integer)
 
```

### Determining the Most Popular Words
 
<div>
After going through ~7900 headlines, these are the most popular words! It's extremely fascinating, I know. 
</div>


```{r, first graph}
titledata %>%
  select(title, category) %>%
  slice(1:7900) %>% 
  mutate(title = strsplit(as.character(title), " ")) %>% 
  unnest(title) %>% 
  group_by(title) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  slice(1:10) %>% 

ggplot(mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines", 
     subtitle = "Wow! What a diverse range of words, could totally make a headline out of it!", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```
<div>
Hmm... Something about this graph doesn't seem right. Let's clean this data up by removing duplicates, punctuation, and prepositions! That'd give us a better idea of what people enjoy to read about, and allow us to find the best subject to center our article around!
</div>

```{r}
titledata <- read.csv("newstitle1.csv")
removedata <- titledata %>%
  select(title, category) %>%
  slice(1:7900) %>%
  mutate(title = strsplit(as.character(title), " ")) %>%
  unnest(title) %>%
  group_by(title) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>%
  slice(1:50)

newdata <- removedata[c(4, 15, 16, 17, 21, 25, 28, 29, 30, 37),]
ggplot(newdata, mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines (Edited)",
     subtitle = "Painfully obvious what year this is from", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```
<div>
Now, this just SCREAMS 2018. Let's get away from all the specific events that happened this year (mainly just the election) and see what other interesting stuff we can find, so that it's believable any time of the year
</div> 

```{r}
titledata <- read.csv("newstitle1.csv")
removedata <- titledata %>%
  select(title, category) %>%
  slice(1:7900) %>%
  mutate(title = strsplit(as.character(title), " ")) %>%
  unnest(title) %>%
  group_by(title) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>%
  slice(1:50)

newdata2 <- removedata[c(16, 17, 25, 28, 29, 33, 35, 44, 45, 47),]
ggplot(newdata2, mapping = aes(x = reorder(title, total), y = total))+
  geom_col(fill = "darkseagreen3")+
  theme_classic()+
  coord_flip()+
labs(title = "Most Common Words in Fake News Headlines (Non-Politics)",
     subtitle = "Missing Children Cases on the Rise?", y = "Amount of Times it has Appeared in a Headline", x = "Word", caption = "Source: BuzzFeed News")
```

<div>
Alright, now we can work with this. Maybe something like "BREAKING NEWS: FBI says they found 'Man Child' in the woods!"
</div> 

# Investigation 2: Length of Header 

Now we can't forget about the lenght of the title. If it's too short, you won't be able to clickbait people into the article, but if it's too long, people won't even read it, which is not ideal :thumbs:

First, we calculate how many characters are in each header! Here's a small sample: 

```{r}
title_length_data <- titledata %>%
  select(title, fb_engagement) %>%
  drop_na() %>% 
  mutate(title_length = str_length(title))  %>% 
  group_by(title_length) %>% 
  arrange(title_length)
```
```{r}
paged_table(title_length_data)

```

OH NO NOT LARRY :(((( 
But let's get a better representation of this data, shall we? 

```{r}
plotlygraph <- ggplot(title_length_data, mapping = aes(x = title_length, y = fb_engagement, color = fb_engagement, text = paste("Title:", title)))+
  geom_point(alpha = 0.5)+
  scale_color_gradient(low = "red", 
                       high = "blue")+
labs(title = "Correlation between Title Length and Popularity on Facebook", subtitle = "Guess people like 40-75 character titles :)", 
     x = "Length of Title (Characters)", y = "Amount of Facebook Likes", color = "Facebook Likes", 
     caption = "Source: Buzzfeed 2018")
```
```{r}
ggplotly(plotlygraph, tooltip = c("text", "x"))
```


